---
title: "Shaded Regions"
---

```{r, include=FALSE}
library(dygraphs)
```

You can add a shading effect to the graph background for one or more time ranges. This is useful for highlighting periods of time with special properties (e.g. holding periods for securities).

For example, the following code adds a shading effect to the 1920's and 1940's for the New Haven Temperatures graph:


```{r}
dygraph(nhtemp, main = "New Haven Temperatures") %>% 
  dyShading(from = "1920-1-1", to = "1930-1-1") %>%
  dyShading(from = "1940-1-1", to = "1950-1-1")
```

Note that the `from` and `to` parameters must be of type `POSIXct` (or objects that are directly convertible to POSIXct).

You may want to modify the color of the shading to make it more or less subtle. Here's a version of the previous graph with custom colors for each shading:

```{r}
dygraph(nhtemp, main = "New Haven Temperatures") %>% 
  dySeries(label = "Temp (F)", color = "black") %>%
  dyShading(from = "1920-1-1", to = "1930-1-1", color = "#FFE6E6") %>%
  dyShading(from = "1940-1-1", to = "1950-1-1", color = "#CCEBD6")
```

Note that we also changed the color of the series to black so that it contrast well with the custom background colors.

It is also possible to add horizontal shading to a chart. In the example below,
shading is used to show the one standard deviation range for a stock return 
series.

```{r}
library(quantmod)
getSymbols("MSFT", from = "2014-06-01", auto.assign=TRUE)
ret = ROC(MSFT[, 4])
mn = mean(ret, na.rm = TRUE)
std = sd(ret, na.rm = TRUE)
dygraph(ret, main = "Microsoft Share Price") %>% 
  dySeries("MSFT.Close", label = "MSFT") %>%
  dyLimit(mn, color = "red", strokePattern = "solid") %>%
  dyShading(from = mn - std, to = mn + std, axis = "y")
```





