---
title: "Range Selector"
---

```{r, include=FALSE}
library(dygraphs)
```

You can add range selector to the bottom of a dygraph that provides a straightforward interface for panning and zooming. For example:

```{r}
dygraph(nhtemp, main = "New Haven Temperatures") %>% 
  dyRangeSelector()
```

You can also specify an initial date range for the range selector:

```{r}
dygraph(nhtemp, main = "New Haven Temperatures") %>% 
  dyRangeSelector(dateWindow = c("1920-01-01", "1960-01-01"))
```

Note that the `dateWindow` parameter should be a two-element vector of `POSIXct` (or objects that can unambiguously converted to POSIXct).

Several other options affect the appearance of the range selector:

```{r}
dygraph(nhtemp, main = "New Haven Temperatures") %>% 
  dyRangeSelector(height = 20, strokeColor = "")
```

#### Shiny Date Input

Shiny applications can respond to changes in the `dateWindow` via a special `date_window` input value. For example, if the output id of a dygraph is `series` then the current date window
can be read from `input$series_date_window` as an array of two date values (from and to). 

Note that when using the data window input variable you should always check for `NULL` before accessing it, for example:

```
output$from <- renderText({
  if (!is.null(input$dygraph_date_window))
    strftime(input$dygraph_date_window[[1]], "%d %b %Y")      
})
```

See the documentation on [using dygraphs with Shiny](shiny.html#shiny-date-input) for a more complete example.





