---
title: "Event Lines"
---

```{r, include=FALSE}
library(dygraphs)
```

Event lines are a useful way to note points within a time series where noteworthy events occurred. For example, in the following graph we overlay the dates which saw the first deployment of US combat troops to Korea and Vietnam over a plot of US presidential approval ratings: 

```{r}
dygraph(presidents, main = "Quarterly Presidential Approval Ratings") %>%
  dyAxis("y", valueRange = c(0, 100)) %>%
  dyEvent(date = "1950-6-30", "Korea", labelLoc = "bottom") %>%
  dyEvent(date = "1965-2-09", "Vietnam", labelLoc = "bottom")
```

Note that we specify that our event labels go at the bottom of the graph so they don't interfere with the legend, and set the y-axis `valueRange` to ensure that there is adequate room at the bottom for the labels.

Related to event lines are limit lines, which can be used to highlight data 
levels. For example, one could use limit lines to highlight the initial price of
a stock price series.

```{r}
library(quantmod)
getSymbols("MSFT", from = "2014-06-01", auto.assign=TRUE)
dygraph(MSFT[, 4], main = "Microsoft Share Price") %>% 
  dySeries("MSFT.Close", label = "MSFT") %>%
  dyLimit(MSFT[1, 4], color = "red")
```