---
title: "Series Highlighting"
---

```{r, include=FALSE}
library(dygraphs)
```


When users hover their mouse over series and points on the graph a highlight effect appears on the surface of the graph. You can use the `dyHighlight` function to customize how the highlighting appears.

In this example we specify a larger circle size for point highlighting as well as more decisively fade the non-highlighted series. We also request that the highlighting persist even after the mouse leaves the graph area.

```{r}
lungDeaths <- cbind(ldeaths, mdeaths, fdeaths)
dygraph(lungDeaths, main = "Deaths from Lung Disease (UK)") %>%
  dyHighlight(highlightCircleSize = 5, 
              highlightSeriesBackgroundAlpha = 0.2,
              hideOnMouseOut = FALSE)
```

You can also set additional visual options for the highlighted series using `highlightSeriesOpts`. This argument takes a list of named series options to apply to just the currently highlighted series (see the `dySeries` function for the various options that can be set). Here we set the stroke width of highlighted series to 3:


```{r}
dygraph(lungDeaths, main = "Deaths from Lung Disease (UK)") %>%
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 3))
```


