---
title: "Time Zones"
---

```{r, include=FALSE}
library(dygraphs)
library(xts)
```

By default **dygraphs** displays time-series using the time zone of the client workstation. However, you can also choose to use the time zone defined within the underlying **xts** object using the `useDataTimezone` option.

For example, consider the following time-series than includes randomly generated values for each 3 hour period of the first day of 2015 (the series is defined using the GMT time zone):

```{r}
library(xts)
datetimes <- seq.POSIXt(as.POSIXct("2015-01-01", tz="GMT"),
                        as.POSIXct("2015-01-02", tz="GMT"), by="3 hours")
values <- rnorm(length(datetimes))
series <- xts(values, order.by = datetimes, tz="GMT")
```

If we plots this using the default dygraph behavior you'll notice that the series doesn't adhere to the day boundaries exactly because it's plotted using your web browser's current time zone:

```{r}
dygraph(series)
```

However, if we specify the `useDataTimezone` option then it will be plotted using GMT and will adhere exactly to the day boundaries:

```{r}
dygraph(series) %>% 
  dyOptions(useDataTimezone = TRUE)
```





