---
title: "Time Zones"
---

```{r, include=FALSE}
library(dygraphs)
library(xts)
```

By default **dygraphs** displays time-series using the time zone of the client workstation. However, you can also choose to use the time zone defined within the underlying **xts** object using the `useDataTimezone` option.

For example, consider the following time-series than includes randomly generated values for each 3 hour period of the first day of 2015 (the series is defined using the GMT time zone):

```{r}
library(xts)
datetimes <- seq.POSIXt(as.POSIXct("2015-01-01", tz="GMT"),
                        as.POSIXct("2015-01-02", tz="GMT"), by="3 hours")
values <- rnorm(length(datetimes))
series <- xts(values, order.by = datetimes, tz="GMT")
```

If we plots this using the default dygraph behavior you'll notice that the series doesn't adhere to the day boundaries exactly because it's plotted using your web browser's current time zone:

```{r}
dygraph(series)
```

However, by specifying the `labelsUTC` option the series will be displayed in UTC time rather than in the local timezone of the client:

```{r}
dygraph(series) %>% 
  dyOptions(labelsUTC = TRUE)
```

If you'd like to force the series to be rendered using an arbitrary time zone you can use the `useDataTimezone` option to specify that whatever timezone is used in the underlying **xts** object should be carried through to the client display. 

In this example we specify `useDataTimezone` and the units are displayed in GMT because that was the time zone used when constructuring the time series:

```{r}
dygraph(series) %>% 
  dyOptions(useDataTimezone = TRUE)
```



