---
title: "Axis Options"
---

```{r, include=FALSE}
library(dygraphs)
```

You can customize the display of axes using the `dyOptions` function (for global options) and `dyAxis` function (for per-axis options). Here's an example that uses both:

```{r}
dygraph(AirPassengers, main = "Airline Passengers / Month") %>%
  dyAxis("x", pixelsPerLabel = 50, drawGrid = FALSE) %>%
  dyAxis("y", label = "Passengers (Thousands)") %>%
  dyOptions(includeZero = TRUE, 
            axisLineColor = "navy", 
            gridLineColor = "lightblue")
```

Here we use a number of options to customize axis display:

1) The `pixelsPerLabel` option reduced the default spacing between labels on the x-axis (this is sometimes necessary if the default label spacing reuslts in too few labels).

2) The `drawGrid` option turns off the grid for the x axis

3) The `includeZero` option ensures that the y axis is scaled from zero rather than the low-end of it's range of values.

4) The `axisLineColor` and `gridLineColor` options change the colors of axis and grid lines respectively.

There are many more options available that affect axis display. See the documentation on `dyAxis` and `dyOptions` for more details.
