---
title: "Using in R Markdown"
---

```{r, include=FALSE}
library(dygraphs)
```


You can use dygraphs within [R Markdown](http://rmarkdown.rstudio.com) documents just like any other R plotting function. However, rather than a PNG file being included in your document, the JavaScript required to render your dygraph is included. 

Note that since dygraphs are web-based (they use HTML, CSS, and JavaScript) they can only be included in HTML based R Markdown formats (i.e. they can't be used in PDF or Word documents).

#### Figure Size

By default, dygraphs that appear within R Markdown documents respect the default figure size of the document. This means that their size will be the same as that of other standard plots.

Figure sizes are specified in inches and can be included as a global option of the document output format. For example:

<pre class="r"><code>---
title: "My Document"
output:
  html_document:
    fig_width: 6
    fig_height: 4
---
</code></pre>

You can also specify figure sizes on a per-chunk basis. For example, to create a dygraph that is smaller than the default (7x5) you could do this:

<pre class="r"><code>&#96;&#96;&#96;{r, fig.width=6, fig.height=2.5}
dygraph(nhtemp, main = "New Haven Temperatures", ylab = "Temp (F)") 
&#96;&#96;&#96;
</code></pre>

```{r, echo=FALSE, fig.width=6, fig.height=2.5}
dygraph(nhtemp, main = "New Haven Temperatures", ylab = "Temp (F)") 
```

