---
title: "Using in Shiny Applications"
---

The dygraphs package provides the `dygraphOutput` and `renderDygraph` functions to enable use of dygraphs within [Shiny](http://shiny.rstudio.com) applications and R Markdown [interactive documents](http://shiny.rstudio.com/articles/interactive-docs.html). 

Note that using dycharts with Shiny requires a development version of the Shiny package. You can install this using **devtools** as follows:

```{r, eval=FALSE}
devtools::install_github("rstudio/shiny")
```

#### Simple Example

These functions work exactly like the Shiny *plotOutput* and *renderPlot* functions. For example, here's a simple Shiny application that uses these functions:

**ui.R**

```{r, eval=FALSE}
library(dygraphs)

shinyUI(fluidPage(
  
  titlePanel("Predicted Deaths from Lung Disease (UK)"),
  
  sidebarLayout(
    sidebarPanel(
      numericInput("months", label = "Months to Predict", 
                   value = 72, min = 12, max = 144, step = 12),
      selectInput("interval", label = "Prediction Interval",
                  choices = c("0.80", "0.90", "0.95", "0.99"),
                  selected = "0.95"),
      checkboxInput("showgrid", label = "Show Grid", value = TRUE)
    ),
    mainPanel(
      dygraphOutput("dygraph")
    )
  )
))
```

**server.R**

```{r, eval=FALSE}
library(dygraphs)
library(datasets)

shinyServer(function(input, output) {
  
  predicted <- reactive({
    hw <- HoltWinters(ldeaths)
    predict(hw, n.ahead = input$months, 
            prediction.interval = TRUE,
            level = as.numeric(input$interval))
  })
  
  output$dygraph <- renderDygraph({
    dygraph(predicted(), main = "Predicted Deaths/Month") %>%
      dySeries(c("lwr", "fit", "upr"), label = "Deaths") %>%
      dyOptions(drawGrid = input$showgrid)
  })
  
})
```
