---
title: "Using in Shiny Applications"
---

The dygraphs package provides the `dygraphOutput` and `renderDygraph` functions to enable use of dygraphs within [Shiny](http://shiny.rstudio.com) applications and R Markdown [interactive documents](http://shiny.rstudio.com/articles/interactive-docs.html). 

Note that using dygraphs with Shiny requires a recent version of the Shiny package (>= 0.10.2.1) so you should be sure to update Shiny before trying out dygraphs with it.

#### Simple Example

These functions work exactly like the Shiny *plotOutput* and *renderPlot* functions. For example, here's a simple Shiny application that uses these functions:

**ui.R**

```{r, eval=FALSE}
library(dygraphs)

shinyUI(fluidPage(
  
  titlePanel("Predicted Deaths from Lung Disease (UK)"),
  
  sidebarLayout(
    sidebarPanel(
      numericInput("months", label = "Months to Predict", 
                   value = 72, min = 12, max = 144, step = 12),
      selectInput("interval", label = "Prediction Interval",
                  choices = c("0.80", "0.90", "0.95", "0.99"),
                  selected = "0.95"),
      checkboxInput("showgrid", label = "Show Grid", value = TRUE)
    ),
    mainPanel(
      dygraphOutput("dygraph")
    )
  )
))
```

**server.R**

```{r, eval=FALSE}
library(dygraphs)
library(datasets)

shinyServer(function(input, output) {
  
  predicted <- reactive({
    hw <- HoltWinters(ldeaths)
    predict(hw, n.ahead = input$months, 
            prediction.interval = TRUE,
            level = as.numeric(input$interval))
  })
  
  output$dygraph <- renderDygraph({
    dygraph(predicted(), main = "Predicted Deaths/Month") %>%
      dySeries(c("lwr", "fit", "upr"), label = "Deaths") %>%
      dyOptions(drawGrid = input$showgrid)
  })
  
})
```


#### Shiny Date Input

Shiny applications can respond to changes in the `dateWindow` via a special `date_window` input value. For example, if the output id of a dygraph is `series` then the current date window
can be read from `input$series_date_window` as an array of two date values (from and to). For example, here's another variation of the simple application from above that displays the current from/to range:

**ui.R**
```r
library(dygraphs)

shinyUI(fluidPage(
  
  titlePanel("Predicted Deaths from Lung Disease (UK)"),
  
  sidebarLayout(
    sidebarPanel(
      numericInput("months", label = "Months to Predict", 
                   value = 72, min = 12, max = 144, step = 12),
      selectInput("interval", label = "Prediction Interval",
                  choices = c("0.80", "0.90", "0.95", "0.99"),
                  selected = "0.95"),
      checkboxInput("showgrid", label = "Show Grid", value = TRUE),
      hr(),
      div(strong("From: "), textOutput("from", inline = TRUE)),
      div(strong("To: "), textOutput("to", inline = TRUE)),
      br(),
      helpText("Click and drag to zoom in (double click to zoom back out).")
    ),
    mainPanel(
      dygraphOutput("dygraph")
    )
  )
))
```

**server.R**

```r
library(dygraphs)
library(datasets)

shinyServer(function(input, output) {
  
  predicted <- reactive({
    hw <- HoltWinters(ldeaths)
    predict(hw, n.ahead = input$months, 
            prediction.interval = TRUE,
            level = as.numeric(input$interval))
  })
  
  output$dygraph <- renderDygraph({
    dygraph(predicted(), main = "Predicted Deaths/Month") %>%
      dySeries(c("lwr", "fit", "upr"), label = "Deaths") %>%
      dyOptions(drawGrid = input$showgrid)
  })
  
  output$from <- renderText({
    if (!is.null(input$dygraph_date_window))
      strftime(input$dygraph_date_window[[1]], "%d %b %Y")      
  })
  
  output$to <- renderText({
    if (!is.null(input$dygraph_date_window))
      strftime(input$dygraph_date_window[[2]], "%d %b %Y")
  })  
})
```




