---
title: "Using in Shiny Applications"
---

The dygraphs package provides the `dygraphOutput` and `renderDygraph` functions to enable use of dygraphs within [Shiny](http://shiny.rstudio.com) applications and R Markdown [interactive documents](http://shiny.rstudio.com/articles/interactive-docs.html). 

Note that using dycharts with Shiny requires a development version of the Shiny package. You can install this using **devtools** as follows:

```{r, eval=FALSE}
devtools::install_github("rstudio/shiny")
```

#### Simple Example

These functions work exactly like the Shiny *plotOutput* and *renderPlot* functions. For example, here's a simple Shiny application that uses these functions:

**ui.R**

```{r, eval=FALSE}
library(dygraphs)

shinyUI(fluidPage(
  
  titlePanel("Shiny dycharts"),
  
  sidebarLayout(
    
    sidebarPanel(
      checkboxInput(inputId = "males", value = TRUE,
                    label = "Males Series"),
      checkboxInput(inputId = "females", value = TRUE,
                    label = "Females Series")
    ),
    
    mainPanel(
      dygraphOutput("dygraph")
    )
  )
))
```

**server.R**

```{r, eval=FALSE}
library(dygraphs)
library(datasets)

shinyServer(function(input, output) {
  
  lungDeaths <- reactive({
     if (input$males && input$females)
       cbind(ldeaths, mdeaths, fdeaths)
     else if (input$males)
       cbind(ldeaths, mdeaths)
     else if (input$females)
       cbind(ldeaths, fdeaths)
     else
       ldeaths
  })
  
  output$dygraph <- renderDygraph({

    dygraph(lungDeaths(), 
            main = "Monthly Deaths from Lung Diseases (UK)")
    
  })
})
```
