---
title: "Using dygraphs"
---

```{r loadpkg, include=FALSE}
library(dygraphs)
```

```{r chunkopts, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Getting Started

The `{dygraphs}` package is an R interface to the [dygraphs](http://dygraphs.com) JavaScript charting library. It provides rich facilities for charting time-series data in R, including:

- Automatically plots [xts](https://cran.rstudio.com/web/packages/xts/index.html) time series objects (or any object convertible to xts).

- Highly configurable axis and series display (including optional second Y-axis).

- Rich interactive features including [zoom/pan](gallery-range-selector.Rmd) and series/point [highlighting](gallery-series-highlighting.Rmd).

- Display [upper/lower bars](gallery-upper-lower-bars.Rmd) (e.g. prediction intervals) around series.

- Various graph overlays including [shaded regions](gallery-shaded-regions.Rmd), [event lines](gallery-event-lines.Rmd), and point [annotations](gallery-annotations.Rmd).

- Use at the R console just like conventional R plots (via RStudio Viewer).

- Seamless embedding within Quarto/R Markdown documents and Shiny web applications.

You can use `{dygraphs}` at the R console, within R Markdown documents, and within Shiny applications. There are a few demos of `{dygraphs}` below as well as quite a few others in the articles section of this website.

Here's a simple `dygraph()` created from a multiple time series object:

```{r}
library(dygraphs)
lungDeaths <- cbind(mdeaths, fdeaths)
dygraph(lungDeaths)
```

Note that this graph is fully interactive: as your mouse moves over the series individual values are displayed. You can also select regions of the graph to zoom into (double-click zooms out).

You can customize dygraphs by piping additional commands onto the original `dygraph()` object. Here we pipe a `dyRangeSelector()` onto our original graph:

```{r}
dygraph(lungDeaths) %>% dyRangeSelector()
```

Note that this example uses the `%>%` (or "pipe") operator from the [magrittr](http://cran.r-project.org/web/packages/magrittr/vignettes/magrittr.html) package to compose the `dygraph()` with the range selector. You use a similar syntax to customize axes, series, and other options. For example:

```{r}
dygraph(lungDeaths) %>%
  dySeries("mdeaths", label = "Male") %>%
  dySeries("fdeaths", label = "Female") %>%
  dyOptions(stackedGraph = TRUE) %>%
  dyRangeSelector(height = 20)
```

Many options for customizing series and axis display are available. It's even possible to combine multiple lower/value/upper style series into a single display with shaded bars. Here's an example that illustrates shaded bars, specifying a plot title, suppressing the drawing of the grid for the x axis, and the use of a custom palette for series colors:

```{r}
hw <- HoltWinters(ldeaths)
predicted <- predict(hw, n.ahead = 72, prediction.interval = TRUE)

dygraph(predicted, main = "Predicted Lung Deaths (UK)") %>%
  dyAxis("x", drawGrid = FALSE) %>%
  dySeries(c("lwr", "fit", "upr"), label = "Deaths") %>%
  dyOptions(colors = RColorBrewer::brewer.pal(3, "Set1"))
```

## RMarkdown

You can use `{dygraphs}` within [R Markdown](http://rmarkdown.rstudio.com) documents just like any other R plotting function. However, rather than a PNG file being included in your document, the JavaScript required to render your `dygraph()` is included. 

Note that since `{dygraphs}` are web-based (they use HTML, CSS, and JavaScript) they can only be included in HTML based R Markdown formats (i.e. they can't be used in PDF or Word documents).

By default, `{dygraphs}` that appear within R Markdown documents respect the default figure size of the document. This means that their size will be the same as that of other standard plots.

Figure sizes are specified in inches and can be included as a global option of the document output format. For example:

```
---
title: "My Document"
output:
  html_document:
    fig_width: 6
    fig_height: 4
---
```

You can also specify figure sizes on a per-chunk basis. For example, to create a `dygraph()` that is smaller than the default (7x5) you could do this:

<pre class="r"><code>&#96;&#96;&#96;{r, fig.width=6, fig.height=2.5}
dygraph(nhtemp, main = "New Haven Temperatures", ylab = "Temp (F)") 
&#96;&#96;&#96;
</code></pre>

```{r markdown, echo=FALSE, fig.width=6, fig.height=2.5}
dygraph(nhtemp, main = "New Haven Temperatures", ylab = "Temp (F)")
```

## Shiny

The `{dygraphs}` package provides the `dygraphOutput()` and `renderDygraph()` functions to enable use of `dygraph()` within [Shiny](http://shiny.rstudio.com) applications. These functions work exactly like the `shiny::plotOutput()` and `shiny::renderPlot()` functions. For example, here's a simple Shiny application that uses these functions:

**ui.R**

```r
library(shiny)
library(bslib)
library(dygraphs)

ui <- page_sidebar(
  title = "Predicted Deaths from Lung Disease (UK)",
  sidebar = sidebar(
    numericInput(
      "months",
      label = "Months to Predict",
      value = 72,
      min = 12,
      max = 144,
      step = 12
    ),
    sliderInput(
      "interval",
      label = "Prediction Interval",
      min = 0.8,
      max = 0.99,
      value = 0.95,
      step = 0.01
    ),
    checkboxInput("showgrid", label = "Show Grid", value = TRUE)
  ),
  dygraphOutput("dygraph")
)
```

**server.R**

```r
library(shiny)
library(dygraphs)
library(datasets)

server <- function(input, output) {
  predicted <- reactive({
    hw <- HoltWinters(ldeaths)
    predict(
      hw,
      n.ahead = input$months,
      prediction.interval = TRUE,
      level = input$interval
    )
  })
  output$dygraph <- renderDygraph({
    dygraph(predicted(), main = "Predicted Deaths/Month") %>%
      dySeries(c("lwr", "fit", "upr"), label = "Deaths") %>%
      dyOptions(drawGrid = input$showgrid)
  })
}
```

Two Shiny input bindings are made available by dygraphs to allow dynamic responses to user actions:

1. A `date_window` input binding which responds to changes in the selected/zoomed `dateWindow`.

2. A `click` input binding which responds to mouse clicks and makes available the value on the x-axis that the click corresponds to as well as the closest x,y point to the click.

The names of the input bindings are the shiny ID combined with the name of the input (e.g. `mydygraph_data_window` or `mydygraph_click`). For example, here's another variation of the simple application from above that displays the current from/to range as well as responds to click events:

**ui.R**

```r
library(shiny)
library(bslib)
library(dygraphs)

ui <- page_sidebar(
  title = "Predicted Deaths from Lung Disease (UK)",

  sidebar = sidebar(
    numericInput(
      "months",
      label = "Months to Predict",
      value = 72,
      min = 12,
      max = 144,
      step = 12
    ),
    sliderInput(
      "interval",
      label = "Prediction Interval",
      min = 0.8,
      max = 0.99,
      value = 0.95,
      step = 0.01
    ),
    checkboxInput("showgrid", label = "Show Grid", value = TRUE),
    hr(),
    div(strong("From: "), textOutput("from", inline = TRUE)),
    div(strong("To: "), textOutput("to", inline = TRUE)),
    div(strong("Date clicked: "), textOutput("clicked", inline = TRUE)),
    div(strong("Nearest point clicked: "), textOutput("point", inline = TRUE)),
    br(),
    helpText("Click and drag to zoom in (double click to zoom back out).")
  ),
  dygraphOutput("dygraph")
)
```

**server.R**

```r
library(shiny)
library(dygraphs)
library(datasets)

server <- function(input, output) {
  predicted <- reactive({
    hw <- HoltWinters(ldeaths)
    predict(
      hw,
      n.ahead = input$months,
      prediction.interval = TRUE,
      level = input$interval
    )
  })

  output$dygraph <- renderDygraph({
    dygraph(predicted(), main = "Predicted Deaths/Month") %>%
      dySeries(c("lwr", "fit", "upr"), label = "Deaths") %>%
      dyOptions(drawGrid = input$showgrid)
  })

  output$from <- renderText({
    strftime(req(input$dygraph_date_window[[1]]), "%d %b %Y")
  })

  output$to <- renderText({
    strftime(req(input$dygraph_date_window[[2]]), "%d %b %Y")
  })

  output$clicked <- renderText({
    strftime(req(input$dygraph_click$x), "%d %b %Y")
  })

  output$point <- renderText({
    paste0(
      'X = ',
      strftime(req(input$dygraph_click$x_closest_point), "%d %b %Y"),
      '; Y = ',
      req(input$dygraph_click$y_closest_point)
    )
  })
}
```
