---
title: "Colored Ribbons"
---

Ribbon is a horizontal band of colors that runs through the chart. It can be useful
to visualize categorical variables
(http://en.wikipedia.org/wiki/Categorical_variable) that change over time (along the
x-axis). For example multiple states of economy like "bust", "recession", "recovery",
"boom" can be encoded as `[0, 1, 2, 3]` respectively (or normalized as `[0, 0.33, 0.66,
1]`) and assigned colors `["red", "orange", "green", "purple"]`.

The following chart contains a colored ribon at the bottom. The position of ribbon is
set with `top` and `bottom` parameters of `dyRibbon` function, `0` means the very
bottom of chart while `1` represents a very top.

```{r setup, include=FALSE}
library(dygraphs)
```

```{r}
library(quantmod)

getSymbols("SPY", from = "2016-12-01", auto.assign=TRUE)

difference <- SPY[, "SPY.Open"] - SPY[, "SPY.Close"]
decreasing <- which(difference < 0)
increasing <- which(difference > 0)

dyData <- SPY[, "SPY.Close"]

ribbonData <- rep(0, nrow(dyData))
ribbonData[decreasing] <- 0.5
ribbonData[increasing] <- 1

dygraph(dyData) %>%
    dyRibbon(data = ribbonData, top = 0.1, bottom = 0.02)
```

It is also possible to feed ribbon with data using a parser written in JavaScript.
Parser has the following signature `function (rawData, dygraphInstance)` and must
return an array. The following example uses such parser to make up a ribbon, also it
uses custom palette:

```{r}
parser <- "function(rawData) {
  var openIdx = 1;
  var closeIdx = 4;
  var ribbonData = [];

  for (var i = 0; i < rawData.length; i++) {
    var row = rawData[i];
    var open = row[openIdx];
    var close = row[closeIdx];

    if (open < close) {
        ribbonData.push(0.5);
    } else if (open > close) {
        ribbonData.push(1);
    } else {
        ribbonData.push(0);
    }
  }
  return ribbonData;
}"

dygraph(SPY[, c("SPY.Open", "SPY.High", "SPY.Low", "SPY.Close")]) %>%
    dyRibbon(parser = parser,
             palette = c("#efefef", "#ffe6e6", "#ccebd6"))
```
