---
title: "Plugins"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE)
library(dygraphs)
```

You can use dygraphs plugins to customize the appearance of dygraphs as well as add new interactive behaviors. Plugins are extensions to the core dygraphs JavaScript library and are also written in JavaScript. For additional information on creating dygraphs plugins see <https://github.com/danvk/dygraphs/tree/master/src/plugins>.

Once you've created a dygraphs plugin you can use the `dyPlugin` function to create an R wrapper function for it. Examples of R wrappers for two simple dygraphs plugins are provided below.

#### Simple Example

The "Unzoom" dygraphs plugin adds a "Reset Zoom" button to the graph when it's displaying in a zoomed state (this is a bit more discoverable than the default double-click gesture for unzooming). The JavaScript source code for the Unzoom plugin is here: <https://github.com/rstudio/dygraphs/blob/master/inst/examples/plugins/unzoom.js>.

Here's how you'd create an R function to wrap the unzoom plugin:

```{r}
dyUnzoom <-function(dygraph) {
  dyPlugin(
    dygraph = dygraph,
    name = "Unzoom",
    path = system.file("examples/plugins/unzoom.js", package = "dygraphs")
  )
}
```

The plugin can now be used directly within a dygraph pipeline along with other dygraphs functions:

```{r}
dygraph(ldeaths) %>% 
  dyRangeSelector() %>% 
  dyUnzoom() 
```

Try zooming the dygraph and note that a "Reset Zoom" button now appears when the graph is in the zoomed state.

#### Plugin Options

The dyCrosshair plugin draws a crosshair line over the point closest to the mouse when the user hovers over the graph (see the JavaScript source code for the plugin here: <https://github.com/rstudio/dygraphs/blob/master/inst/examples/plugins/unzoom.js>). The plugin includes a "direction" option that is provided as an argument to the R wrapper function and then forwarded to the plugin using the "options" argument to `dyPlugin`.

```{r}
dyCrosshair <- function(dygraph, 
                        direction = c("both", "horizontal", "vertical")) {
  dyPlugin(
    dygraph = dygraph,
    name = "Crosshair",
    path = system.file("examples/plugins/crosshair.js", 
                       package = "dygraphs"),
    options = list(direction = match.arg(direction))
  )
}
```

The plugin can now be used just like any other dygraphs function and can even be composed with other plugins:

```{r}
dygraph(ldeaths) %>% 
  dyRangeSelector() %>% 
  dyUnzoom() %>% 
  dyCrosshair(direction = "vertical")
```

If you hover over the graph you'll see a vertical crosshair drawn at the current position of the mouse.

#### Distributing Plugins

Plugins for the dygraphs R package consist of a JavaScript source file and an R function that wraps it. If you want to distribute a plugin to other users you should create an R package that includes the JavaScript source file and the R function wrapper. The full path to the plugin's JavaScript source file should be passed to `dyPlugin` using the `system.file` function as illustrated in both of the examples above.

If you've created a plugin that you think is of broad interest to other users please feel free to submit a pull request to incorporate it directly into the [dygraphs](https://github.com/rstudio/dygraphs) package.



