---
title: "Custom Plotters"
---

```{r setup, include=FALSE}
library(dygraphs)
```

You can use dygraphs plotters to customize the appearance of dygraphs.

Once you've created a dygraphs plotter you can use the `dyPlotter` function to create
an R wrapper function for it. Examples of R wrappers for two simple dygraphs plotters
are provided below.

#### Bar Chart

This plotter draws a bar plot rather a line plot.

Here's how you'd create an R function to wrap the Bar Chart plotter:

```{r}
dyBarChart <- function(dygraph) {
  dyPlotter(dygraph = dygraph,
            name = "BarChart",
            path = system.file("plotters/barchart.js",
                               package = "dygraphs"))
}
```

The plotter can now be used directly within a dygraph pipeline along with other
dygraphs functions:

```{r}
dygraph(ldeaths) %>%
  dyRangeSelector() %>%
  dyBarChart()
```

#### Multi-column Bar Chart

This plotter draws multiple column bar chart.

Here's how you'd create an R function to wrap the Bar Chart plotter:

```{r}
dyMultiColumn <- function(dygraph) {
  dyPlotter(dygraph = dygraph,
            name = "MultiColumn",
            path = system.file("plotters/multicolumn.js",
                               package = "dygraphs"))
}
```

The plotter can now be used directly within a dygraph pipeline along with other
dygraphs functions:

```{r}
lungDeaths <- cbind(mdeaths, fdeaths)
dygraph(lungDeaths) %>%
  dyRangeSelector() %>%
  dyMultiColumn()
```
