---
title: "Plotters"
---

```{r setup, include=FALSE}
library(dygraphs)
```

You can use dygraphs plotters to customize the appearance of dygraphs.

Once you've created a dygraphs plotter you can use the `dyPlotter` function to create
an R wrapper function for it. Examples of R wrappers for two simple dygraphs plotters
are provided below.

#### Bar Chart

This plotter draws a bar plot rather a line plot.

Here's how you'd create an R function to wrap the Bar Chart plotter:

```{r}
dyBarChart <- function(dygraph) {
  dyPlotter(dygraph = dygraph,
            name = "BarChart",
            path = system.file("plotters/barchart.js",
                               package = "dygraphs"))
}
```

The plotter can now be used directly within a dygraph pipeline along with other
dygraphs functions:

```{r}
dygraph(ldeaths) %>%
  dyRangeSelector() %>%
  dyBarChart()
```

#### Multi-column Bar Chart

This plotter draws multiple column bar chart.

Here's how you'd create an R function to wrap the Bar Chart plotter:

```{r}
dyMultiColumn <- function(dygraph) {
  dyPlotter(dygraph = dygraph,
            name = "MultiColumn",
            path = system.file("plotters/multicolumn.js",
                               package = "dygraphs"))
}
```

The plotter can now be used directly within a dygraph pipeline along with other
dygraphs functions:

```{r}
lungDeaths <- cbind(mdeaths, fdeaths)
dygraph(lungDeaths) %>%
  dyRangeSelector() %>%
  dyMultiColumn()

```

#### Series Plotters

While the above plotters act on all the underlying data of the dygraph, you can 
also use variations of the plotters to act on only a single series. Several variations
come with the `dygraphs` package.

```{r}
lungDeaths <- cbind(mdeaths, fdeaths)
dygraph(lungDeaths) %>%
  dyRangeSelector() %>%
  dyBarSeries('fdeaths') %>% 
  dyFilledLine('mdeaths')

```

#### Grouped Series Plotters

`dygraphs` comes packaged with a number of group-based plotters.  

Similar to working with just a single series, you can also use custom plotters on a group of data series from the underlying data. Check the documentation under `Plotters` for more inspiration.

```{r}
lungDeaths <- cbind(mdeaths, fdeaths, ldeaths)
dygraph(lungDeaths) %>%
  dyStackedBarGroup(c('ldeaths', 'mdeaths'))

dygraph(lungDeaths) %>%
  dyMultiColumnGroup(c('mdeaths', 'fdeaths'))

lungDeaths <- cbind(mdeaths, fdeaths, ldeaths, adjustment = 100)
dygraph(lungDeaths) %>%
  dyStackedRibbonGroup(c('fdeaths', 'ldeaths')) %>% 
  dyStackedBarGroup(c('adjustment', 'mdeaths'))

```

#### Mix-and-match

Use the plotters to highlight different series, stack only related groups, or whatever!

```{r}
lungDeaths <- cbind(ldeaths, fdeaths, mdeaths,
                    additive = rep.int(200, length(ldeaths)),
                    line = rep.int(3000, length(ldeaths)))
dygraph(lungDeaths) %>%
  dySeries('line', strokePattern = 'dashed') %>%
  dySeries('ldeaths', stepPlot = TRUE) %>%
  dyStackedBarGroup(c('additive', 'mdeaths')) %>%
  dyStackedRibbonGroup(c('fdeaths', 'ldeaths'))

```