---
title: "Using in Shiny Applications"
---

The dygraphs package provides the `dygraphOutput` and `renderDygraph` functions to enable use of dygraphs within [Shiny](http://shiny.rstudio.com) applications and R Markdown [interactive documents](http://shiny.rstudio.com/articles/interactive-docs.html). 

Note that using dygraphs with Shiny requires a recent version of the Shiny package (>= 0.10.2.1) so you should be sure to update Shiny before trying out dygraphs with it.

#### Simple Example

These functions work exactly like the Shiny *plotOutput* and *renderPlot* functions. For example, here's a simple Shiny application that uses these functions:

**ui.R**

```{r, eval=FALSE}
library(dygraphs)

shinyUI(fluidPage(
  
  titlePanel("Predicted Deaths from Lung Disease (UK)"),
  
  sidebarLayout(
    sidebarPanel(
      numericInput("months", label = "Months to Predict", 
                   value = 72, min = 12, max = 144, step = 12),
      selectInput("interval", label = "Prediction Interval",
                  choices = c("0.80", "0.90", "0.95", "0.99"),
                  selected = "0.95"),
      checkboxInput("showgrid", label = "Show Grid", value = TRUE)
    ),
    mainPanel(
      dygraphOutput("dygraph")
    )
  )
))
```

**server.R**

```{r, eval=FALSE}
library(dygraphs)
library(datasets)

shinyServer(function(input, output) {
  
  predicted <- reactive({
    hw <- HoltWinters(ldeaths)
    predict(hw, n.ahead = input$months, 
            prediction.interval = TRUE,
            level = as.numeric(input$interval))
  })
  
  output$dygraph <- renderDygraph({
    dygraph(predicted(), main = "Predicted Deaths/Month") %>%
      dySeries(c("lwr", "fit", "upr"), label = "Deaths") %>%
      dyOptions(drawGrid = input$showgrid)
  })
  
})
```


#### Shiny Inputs

Two Shiny input bindings are made available by dygraphs to allow dynamic responses to user actions:

1. A `date_window` input binding which responds to changes in the selected/zoomed `dateWindow`.

2. A `click` input binding which responds to mouse clicks and makes available the value on the x-axis that the click corresponds to as well as the closest x,y point to the click.

The names of the input bindings are the shiny ID combined with the name of the input (e.g. `mydygraph_data_window` or `mydygraph_click`). For example, here's another variation of the simple application from above that displays the current from/to range as well as responds to click events:

**ui.R**
```r
library(dygraphs)

shinyUI(fluidPage(
  
  titlePanel("Predicted Deaths from Lung Disease (UK)"),
  
  sidebarLayout(
    sidebarPanel(
      numericInput("months", label = "Months to Predict", 
                   value = 72, min = 12, max = 144, step = 12),
      selectInput("interval", label = "Prediction Interval",
                  choices = c("0.80", "0.90", "0.95", "0.99"),
                  selected = "0.95"),
      checkboxInput("showgrid", label = "Show Grid", value = TRUE),
      hr(),
      div(strong("From: "), textOutput("from", inline = TRUE)),
      div(strong("To: "), textOutput("to", inline = TRUE)),
      div(strong("Date clicked: "), textOutput("clicked", inline = TRUE)),
      div(strong("Nearest point clicked: "), textOutput("point", inline = TRUE)),
      br(),
      helpText("Click and drag to zoom in (double click to zoom back out).")
    ),
    mainPanel(
      dygraphOutput("dygraph")
    )
  )
))
```

**server.R**

```r
library(dygraphs)
library(datasets)

shinyServer(function(input, output) {
  
  predicted <- reactive({
    hw <- HoltWinters(ldeaths)
    predict(hw, n.ahead = input$months, 
            prediction.interval = TRUE,
            level = as.numeric(input$interval))
  })
  
  output$dygraph <- renderDygraph({
    dygraph(predicted(), main = "Predicted Deaths/Month") %>%
      dySeries(c("lwr", "fit", "upr"), label = "Deaths") %>%
      dyOptions(drawGrid = input$showgrid)
  })
  
  output$from <- renderText({
    strftime(req(input$dygraph_date_window[[1]]), "%d %b %Y")      
  })
  
  output$to <- renderText({
    strftime(req(input$dygraph_date_window[[2]]), "%d %b %Y")
  })
  
  output$clicked <- renderText({
    strftime(req(input$dygraph_click$x), "%d %b %Y")
  })

  output$point <- renderText({
    paste0('X = ', strftime(req(input$dygraph_click$x_closest_point), "%d %b %Y"), 
         '; Y = ', req(input$dygraph_click$y_closest_point))
  })
})
```




